2H qSIP Calculations

### 2021-09-07 qSIP_calculations.Rmd
Update qSIP_calculations.Rmd

```{r "shaded chromatogram", fig.width=8, fig.height=8}
peaks_mapped_active %>% ggplot(
  aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
  geom_col(aes(width = rt_end - rt_start)) +
  scale_fill_viridis_c(option = "magma") +
  facet_wrap(~inc_time_d_str, ncol = 1) +
  geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 1300)) +
  labs(fill = TeX("$^2F$"),
         x = "Retention Time (s)",
         y = "Amplitude (mV)") +
  theme(strip.background = element_blank())
```

```{r}
gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = inc_time_d_str, 
      color = inc_time_d_str, 
      fill = inc_time_d_str)) +
  stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 124,
    size = 3,
    alpha = 1,
    position = position_nudge(y = .03)) +
  geom_text_repel(aes(label = compound), 
                  color = "black", 
                  nudge_y = -0.3, 
                  size = 3) +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Incubation time",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria collected from Alpine Tundra",
       caption = "Soils collected from Niwot Ridge LTER") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
```

>>>>

```{r "shaded chromatogram", fig.width=8, fig.height=8}
p_peaks_mapped_active <- peaks_mapped_active %>% ggplot(
  aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
  geom_col(aes(width = rt_end - rt_start)) +
  scale_fill_viridis_c(option = "magma") +
  facet_wrap(~inc_time_d_str, ncol = 1) +
  geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 1300)) +
  labs(fill = TeX("$^2F$"),
         x = "Retention Time (s)",
         y = "Amplitude (mV)") +
  theme(strip.background = element_blank())

```

```{r}
p_gen_time_dist <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = inc_time_d_str, 
      color = inc_time_d_str, 
      fill = inc_time_d_str)) +
  stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 124,
    size = 3,
    alpha = 1,
    position = position_nudge(y = .03)) +
  geom_text_repel(aes(label = compound), 
                  color = "black", 
                  nudge_y = -0.3, 
                  size = 3) +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Incubation time",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria collected from Alpine Tundra",
       caption = "Soils collected from Niwot Ridge LTER") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())

ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
```
